Twists of supersymmetric gauge theories

### 2019-11-22 paper.tex
organizing 5d section

\begin{prop} \label{CS_diml_red_prop}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
\end{prop}

@@

\begin{prop}
Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
\end{prop}
\begin{proof}
We may assume $X,Y,M=\pt$ as in the previous proof.

@@

%\begin{lemma} \label{CS_diml_red_lemma}
%Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.  Split $C$ as $L \times \RR$, where $L = \RR$ or $S^1$.  The \chris{assuming uniqueness} dimensional reduction of this theory along the map $X \times C \to X \times L$ is equivalent to the generalized Chern-Simons theory $\map(X \times L_{\mr{dR}}, B\gg)$.
%\end{lemma}

%\begin{lemma} \label{CS_to_BF_diml_red_lemma}
%Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.  The dimensional reduction of this theory along the map $X \times \RR \to X$ is equivalent to the generalized BF type theory $\map(X, T[1]B\gg)$.
%\end{lemma}

@@

As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_lemma}.
\end{proof}

@@

\begin{proof}
We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.  We can do this by by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory.  More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$. Lemma \ref{CS_to_BF_diml_red_lemma} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$

@@

\subsubsection{The Rank 2 Twist}
We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.  We can understand this twist by a second application of Lemma \ref{CS_diml_red_lemma} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.  This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.

@@

\begin{proof}
The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_lemma} twice.
\end{proof}

@@

\subsection{Dimension 7}
The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.  It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.

@@

\subsubsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter}

@@

\subsection{Dimension 5}

\subsubsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}

@@

Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists.
\begin{enumerate}
 \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous subsection.
 \item Rank $2$ square-zero spinors.  Like in dimension 6, these split into two inequivalent classes:
 \begin{enumerate}
 \item Generically, $Q$ is topological.
 \item There is a special locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
 \end{enumerate}
 \item Rank $4$ square-zero spinors.  These supercharges are also topological.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

@@

>>>>

\begin{prop} \label{CS_to_BF_diml_red_prop}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
\end{prop}

@@

\begin{prop} \label{CS_diml_red_prop}
Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
\end{prop}

\begin{proof}
We may assume $X,Y,M=\pt$ as in the previous proof.

@@

@@

As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_prop}.
\end{proof}

@@

\begin{proof}
We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.  We can do this by by applying Lemma \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.  More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$. Lemma \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$

@@

\subsubsection{The Rank 2 Twist}
We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.  We can understand this twist by a second application of Lemma \ref{CS_diml_red_prop} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.  This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.

@@

\begin{proof}
The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_prop} twice.
\end{proof}

@@

\subsection{Dimension 7} \label{7d_section}
The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.  It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.

@@

\subsubsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter} \label{6d_10_section}

@@

\subsection{Dimension 5}
The 5-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 4-dimensional spinor representation of $\Spin(5) \iso \Sp(4)$, and where $W$ is a $2k$-dimensional symplectic vector space.  The maximal supersymmetric gauge theory has $\mc N=2$.  However, there are $\mc N=1$ super Yang-Mills theory for every choice $U$ of symplectic representation of the gauge group.

\subsubsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}
We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.  This is the theory obtained from 6d $\mc N=(1,0)$ super Yang-Mills theory with matter, after dimensional reduction to 5 dimensions.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from section \ref{6d_10_section} to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^1(\RR^5; \gg)$.
 \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
 \item $\gg$-valued fermions: a spinor $\lambda \in \Omega^0(\RR^5; S \otimes W \otimes \gg)$.
 \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes W \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Supersymmetry action:} Let $Q, Q_1$ and $Q_2$ be $\mc N=1$ supercharges.  We can describe the supersymmetry action as follows.
\begin{prop}
The supersymmetry action $I^{(1)} = I^{(1)}_{\mr{gauge}} + I^{(1)}_{\mr{matter}} + I^{(1)}_{\mr{couple}}$ and $I^{(2)} = I^{(2)}_{\mr{gauge}} + I^{(2)}_{\mr{matter}}$ from Section \ref{6d_10_section} restricts to 5-dimensional $\mc N=1$ fields as follows:
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \\
I^{(1)}_{\mr{matter}}(Q) &= \int \\I^{(1)}_{\mr{gauge}}(Q) &= \int \\
I^{(2)}_{\mr{couple}}(Q_1,Q_2) &= \int  \\
I^{(2)}_{\mr{gauge}}(Q_1,Q_2) &= \int \\
I^{(2)}_{\mr{matter}}(Q_1,Q_2) &= \int 
\end{align*}
\end{prop}

\begin{proof}
\chris{...}
\end{proof}

\vspace{-10pt}
\paragraph{Twisting data:}
There is a unique class of square-zero supercharges in the 5d $\mc N=1$ supersymmetry algebra.  Twists by such supercharges are minimal: they are invariant in three directions.  The stabilizer of a minimal supercharge is isomorphic to $\SU(2) \sub \Spin(5)$.

\begin{theorem} \label{5d_holo_twist_theorem}
The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory $\mr{Map}(S \times L_{\mr{dR}}, U//G)$.
\end{theorem}

\begin{proof}
This follows from the calculation of the minimal twist in 6-dimensional $\mc N=(1,0)$ theory in \chris{ref} above, by applying Proposition \ref{CS_diml_red_prop}.
\end{proof}

@@

\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the fields of maximal super Yang-Mills from 10d, or alternatively by restricting the 7d $\mc N=1$ fields from section \ref{7d_section}, to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: A gauge field $A \in \Omega^1(\RR^5; \gg)$, and five scalars $\phi_1 ,\ldots, \phi_5 \in \Omega^1(\RR^5; \gg)$.
 \item Fermions: A pair of spinors $\lambda_1$ and $\lambda_2$ in $\Omega^0(\RR^5; S \otimes W \otimes \gg)$.
\end{itemize}
We could alternatively have obtained these fields by considering the $\mc N=1$ 5d super Yang-Mills theory, with matter valued in the symplectic representation $T^*\gg$.

\vspace{-10pt}
\paragraph{Supersymmetry action:} Let $Q, Q_1$ and $Q_2$ be $\mc N=2$ supercharges.  We can describe the supersymmetry action as follows.
\begin{prop}
The supersymmetry action $I^{(1)}$ and $I^{(2)}$ from \chris{ref} restricts to 5-dimensional $\mc N=1$ fields as
\begin{align*}
I^{(1)}(Q) &= \int \\
I^{(2)}(Q_1,Q_2) &= \int 
\end{align*}
\end{prop}

\begin{proof}
This follows by restricting the 6d $\mc N=(1,1)$ supersymmetry action further to $\mr O(5)$.  Indeed \chris{...}
\end{proof}

\vspace{-10pt}
\paragraph{Twisting data:}
Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists (see \cite[Section 4.5]{ElliottSafronov}).  These supercharges all occur as square zero supercharges in the 6-dimensional $\mc N=(1,1)$ supersymmetry algebra from the previous section.
\begin{enumerate}
 \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous subsection.
 \item Rank $2$ square-zero spinors.  Like in dimension 6, these split into two inequivalent classes:
 \begin{enumerate}
 \item The open locus, consisting of topological supercharges.
 \item There is a special locus consisting of supercharges with 4 invariant directions.  The former class can be realised as a degeneration of this case.
 \end{enumerate}
 \item Rank $4$ square-zero spinors.  These supercharges are also topological.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

@@

Let us describe the partition function of the A-type topological twist appearing at generic points of this family.  
\begin{theorem}
\chris{Something about the Haydys-Witten equations...}
\end{theorem}
